\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-17 public/paper/pyg4ometry.tex
tidy fact file thing at the top
fix incorrect indentation in front of Nature of Problem

move hint about how long the parts should be to comment

Program title consistency with rest of paper

programming languages are Python and C++, not C/C++ (no standalone C,
although arguably as Cython but I would suggest this should fall under
umbrella of Python)

add NumPy to external routines/libraries since we do depend on it quite heavily

\begin{small}
\noindent
{\em Program Title: PYG4OMETRY }                                         		\\
{\em Licensing provisions: GPLv3 }							\\
{\em Programming language: Python, C/C++}                         		\\
{\em External routines/libraries: ANTLR, CGAL, FreeCAD, OpenCascade, SymPy, VTK}           	\\

%{\em Supplementary material:}                                 				\\
  % Fill in if necessary, otherwise leave out.
%{\em Journal reference of previous version:}                  			\\
  %Only required for a New Version summary, otherwise leave out.
%{\em Does the new version supersede the previous version?:}   	\\
  %Only required for a New Version summary, otherwise leave out.
%{\em Reasons for the new version:}							\\
  %Only required for a New Version summary, otherwise leave out.
%{\em Summary of revisions:}*								\\
  %Only required for a New Version summary, otherwise leave out.

{\em Nature of problem(approx. 50-250 words):}\\
Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task. 
Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
available and geometry conversion is difficult or impossible to convert between these simulation tools. 
\\
{\em Solution method(approx. 50-250 words):}\\
Create a Python application programming interface to read and write files of and process the geometry objects and specification 
language used by Geant4 and FLUKA. Form triangular meshes to represent geometrical objects for both visualisation of the 
geometry and advanced approximate geometrical algorithms. Triangular mesh process allows the loading and use of STL and CAD/CAM 
files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from 
FLUKA to Geant4 requires the replacement of infinite surfaces with finite solids.

>>>>

\begin{small}
\noindent
{\em Program Title: \PYGEOMETRY{} }                                         		\\
{\em Licensing provisions: GPLv3 }							\\
{\em Programming language: Python, C++}                         		\\
{\em External routines/libraries: ANTLR, CGAL, FreeCAD, NumPy, OpenCascade, SymPy, VTK} \\
%{\em Supplementary material:}                                 				\\
  % Fill in if necessary, otherwise leave out.
%{\em Journal reference of previous version:}                  			\\
  %Only required for a New Version summary, otherwise leave out.
%{\em Does the new version supersede the previous version?:}   	\\
  %Only required for a New Version summary, otherwise leave out.
%{\em Reasons for the new version:}							\\
  %Only required for a New Version summary, otherwise leave out.
%{\em Summary of revisions:}*								\\
  %Only required for a New Version summary, otherwise leave out.
{\em Nature of problem:}\\  % (approx. 50-250 words)
Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task. 
Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
available and geometry conversion is difficult or impossible to convert between these simulation tools. 
\\
{\em Solution method:}\\  % (approx. 50-250 words)
Create a Python application programming interface to read and write files of and process the geometry objects and specification 
language used by Geant4 and FLUKA. Form triangular meshes to represent geometrical objects for both visualisation of the 
geometry and advanced approximate geometrical algorithms. Triangular mesh process allows the loading and use of STL and CAD/CAM 
files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from 
FLUKA to Geant4 requires the replacement of infinite surfaces with finite solids.
